---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE, 
  error = FALSE, 
  message = FALSE,
  cache = TRUE
)
```

# iso500

<!-- badges: start -->
[![R-CMD-check](https://github.com/emraher/iso500/workflows/R-CMD-check/badge.svg)](https://github.com/emraher/iso500/actions)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of `iso500` is to download data for **Turkey's Top 500 Industrial Enterprises**.

## Installation

You can install `iso500` from [Github](https://github.com/emraher/iso500) with:

``` r
remotes::install_github("emraher/iso500")
```

## Example

There's only one function in the package, `get_iso500(year)`. You can use this function to download data.

```{r example}
library(magrittr)
library(iso500)

# Following code will download 2018 data.
iso500_data <- get_iso500(2018)

head(iso500_data)


```


## Code of Conduct

Please note that the iso500 project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
